Holomorphic field theories and higher algebra

### 2023-08-18 highervertexops.tex
current

Let $J$ be the map
\beqn
J \colon \laurent \to \cP_2
\eeqn
defined by sending an element $a \in \sfA$ to the quadratic functional
\beqn
J_a (\beta \gamma) = \Res(\beta a \gamma) .
\eeqn

\begin{lem}
The following are true of the map $J$.
\begin{enumerate}
\item $J$ is a cochain map.
\item $J$ is $\lie{sl}(2)$-equivariant.
\item For $a,a' \in \laurent$ one has $\{J_a, J_{a'}\} = 0$.
\end{enumerate}
In particular, if we endow $\sfA$ with the structure of an abelian dg Lie algebra then $J$ is a map of dg Lie algebras.
\end{lem}
\begin{proof}
For the first claim observe that
\beqn
J_{\dbar a} (\beta \gamma) = \Res(\beta (\dbar a) \gamma) = \pm \Res((\dbar \beta) a \gamma) \pm \Res(\beta a \dbar \gamma) = J_a (\dbar \beta \gamma) + (-1)^{|\beta|} J_a(\beta \dbar \gamma) 
\eeqn
by (3) in lemma \ref{lem:res}.
\end{proof}

>>>>

Let $J$ be the map
\beqn
J \colon \laurent \to \cP_2
\eeqn
defined by sending an element $\alpha \in \sfA$ to the quadratic functional $J_\alpha \in \cP_2$ defined by
\beqn
J_\alpha (\beta \gamma) = \Res(\beta \alpha \gamma) .
\eeqn

\begin{lem}
Let $\alpha = z_1^m \lambda_2^n$.
Then $J_\alpha$ corresponds to the infinite series
\begin{multline}
J_\alpha = \sum_{a,b \geq 0} \sum_{k=0}^{a+b} c_k^{a,b} \sff^k(z_1^{a+m}\lambda_2^{b+n} \omega) \cdot \sff^{a+b-k} (z_1^b \lambda_2^a) \d^2 z \\
+ \sum_{a,b \geq 0} \sum_{k=0}^{a+b} c_k^{a,b} \sff^k(z_1^{a+m}\lambda_2^{b+n}) \cdot \sff^{a+b-k} (z_1^b \lambda_2^a \omega) \d^2 z ,
\end{multline}
for some constants $c_{k}^{a,b}$.

Similarly, let $\alpha = z_1^m \lambda_2^n \omega$.
Then $J_\alpha$ corresponds to the infinite series
\beqn
J_\alpha = \sum_{a,b \geq 0} \sum_{k=0}^{a+b} c_k^{a,b} \sff^k(z_1^{a+m}\lambda_2^{b+n} \omega) \cdot \sff^{a+b-k} (z_1^b \lambda_2^a \omega) \d^2 z ,
\eeqn
which is of degree $+1$.
\end{lem}

\begin{prop}
The following are true of the map $J$:
\begin{enumerate}
\item $J$ is a cochain map.
\item $J$ is $\lie{sl}(2)$-equivariant.
\item For $a,a' \in \laurent$ one has $\{J_a, J_{a'}\} = 0$.
\end{enumerate}
In particular, if we endow $\sfA$ with the structure of an abelian dg Lie algebra then $J$ is a map of dg Lie algebras.
\end{prop}
\begin{proof}
For the first claim observe that
\beqn
J_{\dbar a} (\beta \gamma) = \Res(\beta (\dbar a) \gamma) = \pm \Res((\dbar \beta) a \gamma) \pm \Res(\beta a \dbar \gamma) = J_a (\dbar \beta \gamma) + (-1)^{|\beta|} J_a(\beta \dbar \gamma) 
\eeqn
by (3) in lemma \ref{lem:res}.
\end{proof}
